NON-London

### 2017-06-25 LowUseEngland.Rmd
Include Suffolk data
Suffolk boostrapped

>>>>

 SuffStrap<- ls(pattern = "CoastWave") %>% map_df(~eval(parse(text=.x))) %>%
   DistribCompareBootstrapper(., 1652, 1000)

SuffStrap %>%
mutate(RatioExvsAct = (RatioExvsAct-1)*100)%>% 
  ggplot(., aes(x= class, y = RatioExvsAct, fill = class)) + geom_boxplot() + 
  labs(title = "Bootstrapped difference from expected number of low-use homes", y = "% difference from expected")
